An asymptotically normal out-of-sample test based on mixed estimation windows

### 2016-10-17 mixedwindow.tex
[#18] Rewrite Lemma A3, part 1 to fix errors
The original proof of Lemma A3 used a false inequality. This commit
changes the proof of the first part. The second and third parts were
proven by 'assertion' and need to be fixed as well.

\begin{proof}[Proof of~\eqref{eq:11}]
We can write
\begin{equation*}
  \Big\lvert \WesA \Big\rvert \leq
  \Big\lVert \ocltb{t} (F_t - F) B \Big\rVert \;
  \omaxb{t} \lVert H_t \rVert.
\end{equation*}
From Lemma~\ref{res:a2}, $\omaxb{t} \lVert H_t \rVert \to^p
0$. \citepos{Jon:97} \clt\ implies that $\ocltb{t} (F_t - F) =
O_p(1)$, establishing~\eqref{eq:11}.
\end{proof}

>>>>

\begin{proof}[Proof of~\eqref{eq:11}]
Choose $\delta > 0$ and $a \in (0,1/2)$ and write
\begin{multline}\label{eq:A3}
  \WesA =
  \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert > \delta\} \\
  + \WesA \Ind\{ \lvert (t - 1)^a B H_t \rvert \leq \delta\}
\end{multline}
For any $c > 0$,
\begin{multline*}
  \Pr\Bigg[ \Big\lvert \WesA \Ind\{ \lvert (t-1)^a B H_t \rvert > \delta\} \Big\rvert > c \Bigg]
  \leq \\ \Pr\Big[\omaxb{t} \lvert (t-1)^a B H_t \rvert > \delta \Big]
\end{multline*}
which converges to zero by Lemma~\ref{res:a2}, so the first summation on
the RHS of~\eqref{eq:A3} converges to zero i.p.

For the second summation,
\begin{equation*}
  \E \Bigg[ \ocltb{t} (F_t - F) B H_t
    \Ind\{\lvert (t-1)^a B H_t \rvert \leq \delta\}\Bigg]^2
   = O\Bigg(\E \Bigg[ \tfrac{\delta}{\sqrt{P}} \osumb{t} \tfrac{F_t - F}{(t-1)^a} \Bigg]^2\Bigg).
\end{equation*}
The expectation on the RHS is of order
$P^{-1} \sum_{t=R'}^{T-1} (t-1)^{-2a}$, since $F_t / (t-1)^a$ is an
$L_2$-mixingale of size $-1/2$ by construction (see the proof of
Lemma~\ref{res:a2} for a more detailed discussion), and converges to
zero by Kronecker's Lemma.
\end{proof}
